%------------------------------------------------------------------------------%
%                                  objectives                                  %
%------------------------------------------------------------------------------%

\clearpage
\section{Objectives}

The objective of the internship is to study the usage of \gls{hh} and the
data-flow graphs in the context of \gls{hpc} applications. One of the objectives
of the project was to use \gls{hh} to accelerate a simulation application called
\gls{fds}.

\gls{hh} is a \gls{hpc} library written in C++ and created at the NIST. It uses
data-flow graphs to express algorithms composed of tasks that can be run
asynchronously. This library will be described in the section \ref{sec:hh}.

\gls{fds} is a fire simulation also created at the NIST. The simulator reads a
configuration file, solve the fluid dynamics equations and output the results
into files that can be analysed directly or used with other programs. Currently,
\gls{fds} is written in Fortran (standard 2018) and it is parallelized with MPI
and OpenMP. The objective is not to study the mathematical model behind the
simulation. This is to understand how the code is organized and how it processes
the data, in order to be able to design a \gls{hh} graph that will orchestrate
the simulation.

Another goal of the internship is to contribute to the development of \gls{hh}.
Currently, the library is not able to run on multiple nodes on clusters. The
current cluster version of \gls{hh} uses MPI to handle communication between the
nodes. However, this requires to serialize the data before the communication. To
solve this problem, it has been proposed to use a serialization library written
at ISIMA during the third year project. The objective will be to optimize the
serialization time and extend the features of the library in order to be able to
use it in \gls{hh}.
