%------------------------------------------------------------------------------%
%                               problem analisys                               %
%------------------------------------------------------------------------------%

\clearpage{}
\section{Problem analysis}

The first step is to understand how to use \gls{hh}. To do that, the easiest way
to do this is by following the tutorials and creating initial programs to
explore the various features of the library.\\

The next step will be to study \gls{fds}'s source code and isolate the different
parts that will be parallelized using \gls{hh}. \gls{fds} is written in Fortran
and some part of the code are already parallelized with MPI or OpenMP.
Originally, the objective was not to rewrite the entire application in C++. We
aimed to keep the original code and split it into different libraries that could
be used in the C++ code. Only a few critical algorithms should have been
entirely rewritten in C++ in order to optimize the performances. All the
preliminary tests were conducted with this approach in mind, however, we will
see that we eventually concluded that this approach was not feasible because of
the technical limitations of the compilers\footnote{These limitations are
imposed by the standard and not the compilers themselves.}. Furthermore, when
the project has been started, our goal was to port \gls{fds} to \gls{hh}
manually. Once again, after some first tests, we finally decided to automate the
process. To do that, our goal is to create a refactoring tool that will perform
\gls{ast} transformations and that will generate the code of the \gls{hh} graph.
This report will briefly describe the specifications of this tool, but it will
not detail its development since this project has just begun. It is good to
mention that this could not have been predicted without a prior knowledge of the
simulation's code, and the first tests that have been made have played an
important role in the definition of the specifications of the tool.\\

Concerning the serialization library, the primary optimization idea was to use
binary serialization instead of a human-readable format. Indeed, the library
originally used a JSON like format, however, the binary one is liter and does
not need the usage of a \gls{parser}. Furthermore, another optimization will be
to use strings instead of streams. Indeed, as we will explain, the streams are
usually implemented with a linked list. They require to frequently access the
RAM of the computer whereas strings are arrays that can be easily loaded in the
CPU cache.\\

Some features will also be added to the library in order to make it more
powerful. The first version liked the support for static and dynamic arrays.
Furthermore, some data structure can be difficult to serialize because of
pointers. A workaround to this issue is to give the possibility to the user to
execute code during the serialization, so the new serializer will accept
functions. Finally, the old version used some macros that was generating a lot
of code and that was very difficult to maintain. This macro needs be removed in
order for the library to be more usable.
