%------------------------------------------------------------------------------%
%                                   the nist                                   %
%------------------------------------------------------------------------------%

\section{The NIST}

The National Institute of Standards and Technology (NIST) is an agency of the
United States Department of Commerce (DOC) \cite{enwiki:nist}. The National
Bureau of Standards (NBS), also known as the National Metrological Institute
(NMI), was founded in 1901, and it was renamed NIST in 1988. The NIST's role is
to promote innovation and industrial competitiveness of the United States. Its
mission is composed of three main core functions: developing measurement
technology and techniques, creating a maintaining standards, and support
advancement in technology. The researches conducted at the institute impact
several areas such as Health, Energy, Manufacturing, Cybersecurity, Artificial
Intelligence, High Performance Calculus, and more. The NIST's facilities are
distributed across two campus located at Gaithersburg in the Maryland and
Boulder in the Colorado.\\

The NIST is composed of five laboratories:

\begin{itemize}
  \item[$\bullet$] The \textit{Physical Measurement Laboratory} (PML) is responsible for
    finding innovative precise measurements methods in physics, chemistry, and
    engineering.

  \item[$\bullet$] The \textit{Material Measurement Laboratory} (MML) perform research on
    materials, nanotechnologies and biomaterials.

  \item[$\bullet$] The \textit{Information Technology Laboratory} (ITL) develops IT
    standards and works mainly on Artificial Intelligence, Cybersecurity and
    High Performance Calculus.

  \item[$\bullet$] The \textit{Communications Technology Laboratory} (CTL) works on core
    network technologies, wireless systems or public safety communications.

  \item[$\bullet$] The \textit{Engineering Laboratory} (EL) works on technology for
    engineered systems in order to enhance economic security and improve quality
    of life.

  \item[$\bullet$] Finally, the \textit{Center for Neutron Research} (NCNR) provides
    world-class neutron measurement capabilities to meet the needs of
    researchers from industry, academia, and government.
\end{itemize}

Each laboratory is subdivided into divisions and the divisions are split into
groups. This internship has been realized in the \textit{Information Systems}
group directed by Walid Keyrouz. This group is a part of the \textit{Software
and Systems} divisions of the Information Technology Laboratory located on the
Gaithersburg campus. The division is directed by Janet E. Madison.
