%------------------------------------------------------------------------------%
%                                  Conclusion                                  %
%------------------------------------------------------------------------------%

\newpage
\section*{Conclusion}

The objective of the project was to optimize the fire simulation \gls{fds} with
\gls{hh}. Another task was to participate the development of \gls{hh} by
optimizing a serialization library originally created during a project at
ISIMA.\\

The port of \gls{fds} to \gls{hh} is not finished yet since we came to the
conclusion that this task was too complicated to be achieved manually. For this
reason, we eventually decided to create a tool that could automate a part of
this task. However, we are only in the early stages of this project and nothing
is implemented yet. Even if we stopped working directly on \gls{fds}, some part
of the simulation have been optimized. Doing this preliminary work was useful to
understand how the simulator works. Moreover, it had a big impact on the
specifications of the tool that we want to make.\\

During the internship, it has been proposed to use the serialization library in
the cluster version of \gls{hh}. Some new features have been implemented, and
some optimizations have been added to the library. Unfortunately, the
serialization is currently a lot slower compared to the best libraries on the
market. A lot of work remains to be done in order to accelerate the simulation,
and reduce the size of the serialized data. However, the library proposes a
unique concept and has a lot of features. If we managed to approach the
performances of the other libraries, we will be able to use it with \gls{hh}.\\

This internship, was a good introduction to the \gls{hpc} world. A lot of
knowledge have been acquired, and a new innovative project have been started.
There are a lot of differences between what was expected to be done and what was
done eventually. However, the work we do in a laboratory is very different from
the one we do in a company. It is not always possible to predict the results
when we start working on a research project.

\addcontentsline{toc}{section}{\protect\numberline{}Conclusion}
\label{lastPage}
\newpage
\pagestyle{empty}
